Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-01 paper.tex
Add printing of textwidth for use in plotting
Add todos

@@

\todo{include eqns for resistive growth rates}
\todo{write discussion on implications of resistive being non-negligible}
\todo{mention somewhere that both instabilities could be present}
\todo{note that the resistive instability may not be feasible at lower eta}
\todo{in caption of figure 8 we say development is stunted by mixing, should soften this statement}
\todo{find values for all missing items in table 1}

>>>>

%textwidth: \the\textwidth

%font: \fontname\font

%fontsize: \the\fontdimen6\font

@@

\todo{save plot of y-vel sliced in x dir FOR REVIEWER}
\todo{make plots of magnetic, gas and total pressure at t=25 for r-3 FOR REVIEWER}
\todo{include eqns for resistive growth rates}
\todo{write piece on how wavenumbers are calculated}
\todo{add $r_s$ to peak growth rate plots}
\todo{fix caption for heating rates}
\todo{write discussion on implications of resistive being non-negligible}
\todo{mention somewhere that both instabilities could be present}
\todo{note that the resistive instability may not be feasible at lower eta}
\todo{in caption of figure 8 we say development is stunted by mixing, should soften this statement}
\todo{find values for all missing items in table 1}
\todo{Find values for heating caused only by flute instability (i.e. at t=30 or something) and add to table}
